### 2008-08-14 doc/client/arcdata.tex
Something

\texttt{ngcp} can perform multi-stream transfers if \texttt{threads}
URL option is specified and server supports it.

@@

\begin{framed}
   Since the job ID is in fact a \verb#gsiftp://# URL of the job
   top directory, you can use \texttt{ngcp} to copy files from the
   job directory at any time.
\end{framed}

Usage examples of \texttt{ngcp} are:

@@

\subsection{ngrm}\label{sec:ngrm}

The \texttt{ngrm}\footnote{In ARC $\leq$ 0.5.28 was called
  \texttt{ngremove}} \index{ngrm}\index{commands:ngrm}
command allows users to erase files at any location specified by a
valid URL.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{ngrm [options] $<$source$>$}
\end{shaded}
\versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level: 0 = some, 1 = more, 2 = a lot \\
    \texttt{-c} & &continue with meta-data even if it failed to delete real file\\
    \texttt{-C} & \textit{cache\_data\_path} & store cached data\\
    Arguments:&&\\
    \texttt{source} && source URL\\
\end{longtable}

\begin{framed}
   A convenient use for \texttt{ngrm} is to erase the files in a data
   indexing catalog (RC, RLS or such), as it will not only remove the
   physical instance, but also will clean up the database record.
\end{framed}

Here is an \texttt{ngrm} example:

@@

\subsection{ngacl}\label{sec:ngacl}

\index{ngacl}\index{commands:ngacl}This command retrieves or modifies
access control information associated with a stored object if service
supports GridSite GACL language~\cite{gacl} for access control.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{ngacl [options] get$|$put $<$URL$>$}
\end{shaded}
\versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
\begin{longtable}{llp{8cm}}
   Options:&&\\
    \texttt{-d, -debug} & \textit{debuglevel} &debug level: 0 = some, 1 = more, 2 = a lot \\
    \texttt{-v} && print version information\\
    \texttt{-h} && short help\\
   Arguments:&&\\
    \texttt{get} &\textit{URL}& get Grid ACL for the object\\
    \texttt{put} &\textit{URL}& set Grid ACL for the object\\
    \texttt{URL} && object URL; curently only gsiftp and sse URLs are supported\\
\end{longtable}

@@

\subsection{ngtransfer}\label{sec:ngtransfer}
\index{ngtransfer}\index{commands:ngtransfer}The \texttt{ngtransfer}
command\footnote{In ARC $\leq$ 0.5.28, was called \texttt{ngrequest}}
initiates direct transfer of data between 2 servers (known as
\textit{third-party transfer}).  
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{ngtransfer [options] $<$destination$>$}
\end{shaded}
\versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
\begin{longtable}{llp{8cm}}
   Options:&&\\
    \texttt{-s, -source} & \textit{URL} & source file URL\\
    \texttt{-d, -debug} & \textit{debuglevel} &debug level: 0 = some, 1 = more, 2 = a lot \\
    \texttt{-v} && print version information\\
    \texttt{-h} && short help\\
   Arguments:&&\\
    \texttt{destination} && destination URL; currently only se:// and
    (gsi)ftp:// are supported\\
\end{longtable}

This command initiates file copy from multiple source instances to a
destination URL. Destination of \texttt{(gsi)ftp} type accepts only
similar kinds of sources.  Destination can also be URL of an Indexing
Service. In such a case, real destinations with suitable protocols are
chosen, when available. Requests are sent to the corresponding
services/servers to initiate file transfer from one of the sources.

\begin{framed}
   Absence of \verb#-s# option is treated as a file replication
   request. In this case, destination must be an Indexing service or
   an SRM.
\end{framed}

Following source URL types are supported: \texttt{http},
\texttt{https}, \texttt{httpg}, \texttt{ftp}, \texttt{gsiftp},
\texttt{rc}, \texttt{rls}, \texttt{se}, \texttt{srm}, \texttt{fireman}
(see Section~\ref{sec:urls} for URL details).

Example:
\begin{verbatim}
    ngtransfer -s http://www.host1.org/dat1  -s gsiftp://host2.org/dir/dat1 \
               se://se.host.org/se_service?new_file_lfn
\end{verbatim}

>>>>

\texttt{arccp} can perform multi-stream transfers if \texttt{threads}
URL option is specified and server supports it.

@@

\begin{framed}
   Since the job ID is in fact a \verb#gsiftp://# URL of the job
   top directory, you can use \texttt{arccp} to copy files from the
   job directory at any time.
\end{framed}

Usage examples of \texttt{arccp} are:

@@

\subsection{arcrm}\label{sec:arcrm}

The \texttt{arcrm}\footnote{In ARC $\leq$ 0.5.28 was called
  \texttt{arcremove}} \index{arcrm}\index{commands:arcrm}
command allows users to erase files at any location specified by a
valid URL.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{ngrm [options] $<$source$>$}
\end{shaded}
\versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level: 0 = some, 1 = more, 2 = a lot \\
    \texttt{-c} & &continue with meta-data even if it failed to delete real file\\
    \texttt{-C} & \textit{cache\_data\_path} & store cached data\\
    Arguments:&&\\
    \texttt{source} && source URL\\
\end{longtable}

\begin{framed}
   A convenient use for \texttt{ngarc} is to erase the files in a data
   indexing catalog (RC, RLS or such), as it will not only remove the
   physical instance, but also will clean up the database record.
\end{framed}

Here is an \texttt{arcrm} example:

@@

\subsection{arcacl}\label{sec:arcacl}

\index{arcacl}\index{commands:arcacl}This command retrieves or modifies
access control information associated with a stored object if service
supports GridSite GACL language~\cite{gacl} for access control.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcacl [options] get$|$put $<$URL$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
    \texttt{-d, -debug} & \textit{debuglevel} &debug level: 0 = some, 1 = more, 2 = a lot \\
    \texttt{-v} && print version information\\
    \texttt{-h} && short help\\
   Arguments:&&\\
    \texttt{get} &\textit{URL}& get Grid ACL for the object\\
    \texttt{put} &\textit{URL}& set Grid ACL for the object\\
    \texttt{URL} && object URL; curently only gsiftp and sse URLs are supported\\
\end{longtable}

@@

\subsection{arctransfer}\label{sec:arctransfer}
\index{arctransfer}\index{commands:arctransfer}The \texttt{arctransfer}
This command is not implemented.

### 2008-08-14 doc/client/arcjob.tex
Something

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcsub [options] $<$task ...$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{ -c, -cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
   \texttt{ -C, -clustlist}&\verb#[-]#textem{filename}&list of sites (clusters) to select or reject\\
   \texttt{ -g, -giisurl}&\textit{url}&URL of a central Information System server (GIIS)\\
   \texttt{ -G, -giislist}&\textit{filename}&list of GIIS URLs\\
   \texttt{ -e, -xrsl}&\textit{filename}&string describing the job to be submitted\\
   \texttt{ -f, -file}&\textit{filename}&file describing the job to be submitted\\
   \texttt{ -o, -joblist}&\textit{filename}&file where the job IDs will be stored\\
   \texttt{ ~~~~-dryrun}&&add dryrun option to the job description\\
   \texttt{ ~~~~-dumpxrsl}&&do not submit -- dump transformed job description to stdout\\
   \texttt{ -t, -timeout}&\textit{time}&timeout for queries (default 40 sec)\\
   \texttt{ -d, -debug}&\textit{debuglevel}&debug level, from -3 (quiet) to 3 (verbose) - default 0\\
   \texttt{ -x, -anonymous}&&use anonymous bind for queries (default)\\
   \texttt{ -X, -gsi}&&use GSI-GSSAPI bind for queries\\
   \texttt{ -v, -version}&&print version information\\
   \texttt{ -h, -help}&&print help page\\
   Arguments:&&\\
   \texttt{ task ...}&&strings or files describing the jobs to be submitted\\
\end{longtable}

\begin{framed}
Some text can be in frames
\end{framed}

A simple \textit{"Hello World"} job would look like

>>>>

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcsub [options] $<$task ...$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{ -c, --cluster}&\verb#[-]#\textit{url}&explicitly select or reject a specific site (cluster)\\
   \texttt{ -i, --indexurl}&\textit{url}&URL of an index server\\
   \texttt{ -e, --jobdescrstring}&\textit{filename}&string describing the job to be submitted\\
   \texttt{ -f, --jobdescrfile}&\textit{filename}&file describing the job to be submitted\\
   \texttt{ -j, --joblist}&\textit{filename}&file where the job IDs will be stored\\
   \texttt{ -D, --dryrun}&&add dryrun option to the job description\\
   \texttt{ -x, --dumpdescription}&&do not submit -- dump transformed job description to stdout\\
   \texttt{ -t, --timeout}&\textit{time}&timeout for queries in seconds (default 20)\\
   \texttt{ -d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE - default WARNING\\
   \texttt{ -U, --unknownattr}&&allow unknown attributes in the job description\\
   \texttt{ -v, --version}&&print version information\\
   \texttt{ -?, --help}&&print help page\\
   Arguments:&&\\
   \texttt{ task ...}&&strings or files describing the jobs to be submitted\\
\end{longtable}

\begin{framed}
The -c and -i arguments accept ``urls'' of the format GRID:URL,

e.g. for index servers:

ARC0:ldap://grid.tsl.uu.se:2135/mds-vo-name=sweden,O=grid

CREAM:ldap://cream.grid.upjs.sk:2170/o=grid

or clusters:

ARC0:ldap://grid.tsl.uu.se:2135/nordugrid-cluster-name=grid.tsl.uu.se,Mds-Vo-name=local,o=grid
\end{framed}

A simple \textit{"Hello World"} job would look like...
